A Framework for Equivalence of Cast Calculi and a new Cast Representation

### 2020-10-05 paper.tex
removed old comment

\todo[inline]{KC: (about the p below) Actually I think twosome's
  composition is structurally recursive but threesomes' is not}
\todo[inline]{JS: Then please go ahead and fix it.}
\todo[inline]{KC: Fixed. 
``Threesomes and supercoercions are good for
mechanized metatheory because their compose operators 
can be written in a structrually recursive form,''}

The published space-efficient cast representations have various
strengths and weaknesses.  The major insight of these systems is a
compose operator for casts which compresses cast information to reduce
space consumption.  Threesomes and supercoercions are good for
mechanized metatheory because their compose operators 
can be written in a structrually recursive form,
% are structurally recursive,
making them easy to define in proof assistants such as
Agda. In contrast, the coercions in normal form have compose operators
that are not structurally recursive, which makes it more difficult to
define in Agda, requiring what amounts to an explicit proof of
termination.
%
On the other hand, coercions in normal form are easier to understand
than threesomes (with their strange labeled bottom type), and
supercoercions (10 different kinds).

>>>>

The published space-efficient cast representations have various
strengths and weaknesses.  The major insight of these systems is a
compose operator for casts which compresses cast information to reduce
space consumption.  Threesomes and supercoercions are good for
mechanized metatheory because their compose operators 
can be written in a structrually recursive form,
making them easy to define in proof assistants such as
Agda. In contrast, the coercions in normal form have compose operators
that are not structurally recursive, which makes it more difficult to
define in Agda, requiring what amounts to an explicit proof of
termination.
%
On the other hand, coercions in normal form are easier to understand
than threesomes (which have a strange labeled bottom type), and
supercoercions (10 different kinds).
